BSOS

### 2014-06-07 Paper.tex
updated booting section

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{listings}
\usepackage{geometry}
\geometry{verbose,tmargin=1.47cm,bmargin=1.47cm,lmargin=1.47cm,rmargin=1.47cm}

@@

\part{Booting Up}

\begin{lstlisting}
Will's stuff goes here.
\end{lstlisting}

>>>>

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{geometry}
\geometry{verbose,tmargin=1.47cm,bmargin=1.47cm,lmargin=1.47cm,rmargin=1.47cm}

@@

\part{Booting Up}
BSOS's bootstrapping process can be classified by architecture.

\paragraph{x86}
On x86 machines, specifically i386 and later, BSOS begins in 16-bit real mode. The strapping sector, which is 512 bytes long, then loads a general descriptor table, or GDT, into memory. That descriptor table is then used to switch the CPU into 32-bit protected mode, whereupon the kernel is loaded.
\begin{figure}[h!]
\centerline{\includegraphics[scale=0.4]{imgs/boot_x86.png}}
\caption{Figure 1: Bootstrapping on i386.}
\end{figure}

\paragraph{ARM}
On ARM-based machines, specifically those with Cortex-M3 processors, the bootstrapping process [...]
